### 2015-09-24 paper/main.tex
rejigged dsc-shrink dsc for new version of dscr; added plot of lfsr and relevant text to paper

@@

To briefly summarize the results in this section:
\begin{enumerate}
\item The UA can produce very different inferences compared with the ZA.
\item The UA can yield conservative estimates of the proportion of true nulls, $\pi_0$, and hence conservative estimates of \lfdr.
\item The UA results in a stable procedure, both numerically and statistically.
\item The UA is somewhat robust to deviations from unimodality.
\end{enumerate}

@@

Figure \ref{fig:ZA} may also be helpful in understanding the interacting role of the UA and the penalty term (\ref{eqn:penalty}) that attempts to make $\pi_0$ as ``large as possible" while remaining consistent with the UA. Specifically, consider the panel of Figure \ref{fig:ZA} that shows \ashr's decomposition of $z$ scores, and imagine increasing $\pi_0$ further. This would increase the null component (dark blue) at the expense of
the alternative component (light blue). Because the null component is $N(0,1)$, and so is biggest at 0, this would eventually create a ``dip" in the light-blue histogram at 0. The role of the penalty term is to push the dark blue component as far as possible, right up to (or, to be conservative, perhaps just past) the point where this dip appears. In contrast the ZA pushes the dark blue component until the light-blue component {\it disappears} at 0.

 \subsubsection*{The UA produces conservative estimates of $\pi_0$ (if it holds)}

 How do these differences influence estimates of the FDR? To address this, we note that  -- in this simple case where the 
 $\shat_j$ are all identical --  the primary driver of differences in FDR estimates among methods is {\it differences in their estimates
 of $\pi_0$}. To see why, observe that, given an estimate $\hat\pi_0$ for $\pi_0$, equation (\ref{eqn:FDRest}) provides a 
 strikingly natural non-parametric estimate for the FDR (provided the denominator is not very small). Thus, 
 although the methods considered here differ from one another in many ways, having estimated $\pi_0$
 they should, if sensible, produce estimates of FDR that agree closely with (\ref{eqn:FDRest}). And, indeed, limited
 empirical checks suggest that this is indeed the case (\url{https://www.github.com/stephens999/ash/examples/qvalue.nonp.rmd}).

Thus, differences in FDR estimates among methods are driven primarily by differences in their estimates of $\pi_0$,
 and so to assess differences in FDR estimates among methods we focus on assessing differences in estimates of $\pi_0$.
Figure \ref{fig:ZA} suggests that, compared with the ZA, the UA will tend to reduce the estimate of $\pi_0$. 
At the same time, provided the UA holds, we hope still to provide ``conservative" estimates of $\pi_0$ (that is,
overestimates of $\pi_0$, which will yield overestimates of the FDR).
To confirm this we performed simulations under various alternative scenarios (i.e. various distributions for the non-zero effects,
$g_1$), and values
for $\pi_0$. The alternative distributions are shown in Figure \ref{fig:pi0sims}a, with details in Table \ref{table:scenarios}.
They range from a ``spiky" distribution -- where many non-zero $\beta$ are
too close to  zero to be reliably detected, making reliable estimation of $\pi_0$ essentially impossible -- to a much
flatter distribution, which is a normal distribution with large variance (``big-normal") -- where most non-zero $\beta$ are easily detected
making reliable estimation of $\pi_0$ easier. We also include one asymmetric distribution (``skew"), and one clearly bimodal distribution (``bimodal"),
which, although we view as often unrealistic, we include to assess robustness of our methods to deviations from the UA.

\begin{figure} 
\begin{center}
\includegraphics[height=2in]{figures/scenarios_density.pdf} 
\includegraphics[height=2in]{figures/pi0_est.pdf} 
\end{center}
\caption{a) Summary of the alternative distributions used for different simulation scenarios. b) Comparison of true and estimated values of $\pi_0$ in these simulated scenarios. In general $\pi_0$ is impossible to estimate accurately, and all methods yield conservative (over-)estimates for $\pi_0$ (deliberately so, to ensure conservative estimates of FDR). As expected, when the UA holds, the \ashr method is least conservative, and hence most accurate. When the UA assumption does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative (less so for ash.u than for ash.n in this case)} \label{fig:pi0sims}
\end{figure}

\begin{table}[!ht]
\begin{tabular}{c c } \toprule
Scenario & Alternative distribution, $g_1$  \\ \midrule
spiky & $0.4 N(0,0.25^2) + 0.2 N(0,0.5^2) + 0.2 N(0,1^2), 0.2 N(0,2^2) $\\
near normal & $2/3 N(0,1^2) + 1/3 N(0,2^2)$ \\
flattop& $(1/7) [N(-1.5,.5^2) + N(-1,.5^2) + N(-.5,.5^2) +$ \\
 &  $N(0,.5^2) +N(0.5,.5^2)  +N(1.0,.5^2) + N(1.5,.5^2)]$  \\
skew & $(1/4) N(-2,2^2) + (1/4) N(-1,1.5^2) +  (1/3) N(0,1^2) + (1/6) N(1,1^2) $\\
big-normal & $N(0,4^2)$ \\ 
bimodal & $0.5 N(-2,1^2) + 0.5 N(2,1^2)$ \\ \bottomrule
\end{tabular}
\caption{Summary of simulation scenarios considered} \label{table:scenarios}
\end{table}

@@

We applied  \qvalue, \locfdr, \mixfdr and \ashr to
estimate $\pi_0$ for each data set. For \ashr we show results for $g$ modelled as a mixture of normal components (``ash.n") 
and a mixture of symmetric uniform components (``ash.u"). (Results using the asymmetric uniforms, which we refer to
as ``half-uniforms", and denote ``ash.hu" in subsequent sections, are here generally similar to ash.u and omitted to avoid over-cluttering figures.)

Figure \ref{fig:pi0sims}b) compares estimated and true values of $\pi_0$ under each Scenario. 
For most scenarios no method reliably estimates $\pi_0$. This is expected because most scenarios include
an appreciable fraction of ``small non-null effects" that are essentially indistinguishable from 0, making accurate
estimation of $\pi_0$ impossible. This is particularly true for the ``spiky" scenario, for example.  The
exception is the ``big-normal" scenario, where the \ashr estimates of $\pi_0$ are quite accurate - made possible by the fact that, in this scenario, most non-zero effects
are very different from zero.

Although accurate estimation of $\pi_0$ is impossible in general, the simulation results demonstrate
that, when the UA holds, \ashr consistently provides substantially smaller, more accurate, estimates of $\pi_0$, than existing methods. 
As noted above, this means that estimates of FDR from \ashr will also be smaller and more accurate under these scenarios (while
remaining conservative).
When the UA assumption does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative.
We view such a strong bimodal scenario as rather unlikely in most applications where FDR methods
are used; nonetheless, users may find it reassuring that even in this case the results from \ashr should not be horribly misleading.

@@

@@

The EM algorithm, which we use here to fit our model, is notorious for convergence to local optima. 
However, in this case, over hundreds of applications of the procedure, we observed no obvious serious problems 
caused by such behaviour. To quantify this, we ran \ashr 10 times on each of the 600 simulated datasets above using a random initialization for $\pi$,
in addition running it using our default initialization procedure (see Implementation details). We then compared the largest
log-likelihood achieved across all 11 runs with the log-likelihood achieved by the default run.
When using a mixture of normals (ash.n) the results were extremely stable: 96\% showed a negligible log-likelihood difference (< 0.02), 
and the largest difference was 0.8. When using mixtures of uniforms (ash.u,ash.hu) results were slightly less stable: 89\% showed a negligible log-likelihood difference (<0.02),
and 6\% of runs showed an appreciable log-likelihood difference (>1), with the largest difference being 5.0. However, perhaps suprisingly, 
even for this largest difference results from the default run (e.g. the $\lfsr$ values, and the posterior means) were in other ways virtually indistinguishable from the results from the run with the highest log-likelihood \url{github.com/stephens999/ash/dsc-robust/summarize_dsc_robust.rmd}.

@@

Although we have focussed on estimating the FDR, an important advantage of
our EB approach based on modelling the effects $\beta_j$ (rather than $p$ values or $z$ scores)  is that it
can estimate the {\it size} of each effect $\beta_j$.
Specifically, it provides a posterior distribution for each $\beta_j$, which can be used
to address any question about the effect sizes, including, for example, ``which effects likely exceed $T$'', where
$T$ is some effect threshold of interest (and ``likely" can be quantified by whatever probability threshold is desired). 
Importantly, because the posterior distribution for $\beta_j$ depends on the ``prior" effect-size distribution $g$, which is estimated from {\it all} the observations,
this posterior reflects information from all the observations and not only from the observation $\bhat_j$. 
In our case, because we assume $g$ to be unimodal about zero, this prior always ``shrinks" the posterior distributions
towards zero, with the strength of the shrinkage being estimated from the data.
Further, because the posterior distribution is, by definition,
conditional on the observed data, inferences based on posterior distributions are also valid Bayesian inferences for any subset of the effects that have
been selected based on the observed data. This kind of ``post-selection" validity is much harder to achieve in the frequentist paradigm.
In particular the posterior distribution solves the (Bayesian analogue of the) ``False Coverage Rate" problem posed by
\cite{benjamini2005false} which \cite{efron2008microarrays} summarizes as follows: ``having applied FDR methods to select a set of nonnull cases,
how can confidence intervals be assigned to the true
effect size for each selected case?". \cite{efron2008microarrays} notes the potential for EB approaches to tackle this problem,
and \cite{zhao2012empirical} consider in detail the case where the non-null effects are normally distributed.
%but also notes the difficulties of implementing a stable general algorithm.

The ability of the EB approach to provide shrunken posterior distributions and interval estimates for parameters
that are valid ``post-selection" is extremely attractive in principle.
But its usefulness in practice
depends on reliably estimating the distribution $g$. Estimating $g$ is a ``deconvolution problem",
which are notoriously difficult to solve in general. Indeed, Efron emphasises
the difficulties of implementing a stable general algorithm, noting in his rejoinder
``the effort foundered on practical difficulties involving the perils of deconvolution... Maybe I am trying
to be overly nonparametric in constructing the empirical
Bayes Fdr estimates, but it is hard to imagine a
generally satisfactory parametric formulation..." (\cite{efron2008microarrays} rejoinder, p46).
The key point we want to emphasise here is that {\it if we restrict ourselves
to settings where we can assume that $g$ is unimodal}
then a stable non-parametric approach becomes not only possible, but indeed quite straightforward.
While not meeting Efron's desire for an entirely general nonparametric approach, we believe 
that these settings include many cases of practical interest.

To illustrate this, Figure \ref{fig:egcdf} compares
the estimated $g$ from our method for each of the simulation scenarios above with the 
estimated $g$ from \mixfdr which does not make the UA (and which models $g$ as a mixture of $J$ normal distributions, with $J=3$ by default).
Even with only one simulated example for each scenario, the greater reliability of estimates afforded
by the UA is immediately apparent. In particular the greater tendency for \mixfdr to overestimate $\pi_0$ is readily visible in its behaviour at 0.
And the estimated cdf from \mixfdr often has a vertical (or almost vertical)
segment at some non-zero location, indicative of a concentration of density in the estimated $g$ at that location. This corresponds to
one of the 3 mixture components being estimated to be centered at that location with very small variance. 
The UA prevents this kind of ``irregular" behaviour, effectively requiring $g$ to be somewhat smooth.
While the UA is not the only way to achieve this, we find it an attractive, simple and effective approach.

Interestingly, even in the ``bimodal" scenario where the UA is severely contradicted, the estimated $g$ from $\ashr$ 
is visually more accurate than that from \mixfdr: although \mixfdr is capable, in principle, of fitting the multiple modes of $g$, it does not do this well here. We believe this
mostly reflects the fact that the noise level is sufficiently large to make reliable estimation of the multiple modes difficult, rather than 
fundamental deficiencies of \mixfdr. Indeed, in multi-modal simulations where the multiple modes are sufficiently well-spaced
to be clearly visible in the observed $\bhat$, \mixfdr fits these modes (Supplementary Information; 
\url{dsc-shrink/check_mixfdr_lownoise.rmd}). Of course, we would not advocate the UA in settings where multi-modality is 
clearly visible in the observed $\bhat$.

We note one caveat on the accuracy of estimated $g$: \ashr tends to systematically
overestimate the mass of $g$ near zero, due to our deliberate use of a penalty term (\ref{eqn:penalty}) to avoid under-estimation of $\pi_0$.
On careful inspection, this is visually apparent in Figure \ref{fig:egcdf}: the estimated cdf is generally below the true cdf just to the left of zero,
and above the true cdf just to the right of zero. Averaging the cdf over many replicates confirms this systematic effect (Figure \ref{fig:egcdf}b),
and applying our methods without the penalty term removes this systematic effect, although at the cost of sometimes 
under-estimating $\pi_0$ (Figure \ref{fig:egcdf}c).

@@

\subsubsection*{Calibration of posterior distributions}

To quantify the effects of errors in estimates of $g$ we examine the calibration of the resulting posterior distributions (averaged over all 100 simulations in each Scenario). 
Specifically we examine the empirical coverage of nominal lower 95\% credible bounds for a) all observations; b) significant negative discoveries; c) significant positive discoveries.  We examine only lower bounds because the results for upper bounds follow by 
symmetry (except for the one asymetric scenario). We separately examine positive and negative discoveries because the lower bound plays a different role
in each case: for negative discoveries the lower bound is typically large and negative and limits how big (in absolute value) 
the effect could be; for positive discoveries the lower bound 
is positive, and limits how small (in absolute value) the effect could be. Intuitively, the lower bound for negative discoveries depends on the accuracy of $g$ in its tail,
whereas for positive discoveries it is more dependent on the accuracy of $g$ in the center.

The results are shown in Table \ref{tab:coverage}.  
As noted above, our use of a penalty term to avoid underestimating $\pi_0$ means that the estimated $g$s tends to have, systematically, slightly too much mass near 0.
If the prior has too much mass near 0 then so will the posterior, so we should expect posterior intervals may also be ``over-shrunk" towards zero. 
The effect of overshrinking on the left tail area is different for ``negative discoveries" and ``positive discoveries": for negative discoveries the lower credible bound will be negative and overshrinking will move the bound towards zero, making the left tail too big; for positive discoveries, the lower confidence bound will be positive, and  
overshrinking will move it toward zero, making the tail too small. In the context of reliably identifying ``large" effects we might worry more about under-shrinkage, 
and be prepared to put up with some overshrinkage to avoid it.

@@

\subsubsection*{Problems with removing the penalty term in the half-uniform case}

When we tried using no penalty term in the half-uniform case we came across an unanticipated problem: when the data
are nearly null, the estimated $g$ converges, as expected and desired, to a distribution where almost all the mass is near 0, but
sometimes all this mass is concentrated almost entirely just to one side (left or right) or 0. This can have a very profound effect on the local false sign rate:
for example, if all the mass is just to the right of 0 then all observations will be assigned a very high probability of being positive (but very small),
and a (misleading) low local false sign rate. For this reason we do not recommend use of the half-uniform with no penalty.

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\centering\input{tables/scoverage_all.tex}
	\caption{All observations. Coverage rates are generally satisfactory, except for the extreme ``spiky" scenario. This is due to the penalty term (\ref{eqn:penalty}) which tends to cause over-shrinking towards zero; removing this penalty term produces coverage rates closer to the nominal levels for uniform and normal methods. (Removing the penalty in the half-uniform case can lead to unexpected problems explained in Section \ref{sec:unexpected}).}
\end{subtable}

@@

\caption{Table of empirical coverage for nominal 95\% lower credible bounds (methods with penalty term). } \label{tab:coverage}
\end{table}

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\input{tables/scoverage_all_nopen.tex}
	\caption{All observations}
\end{subtable}

\begin{subtable}{\textwidth}
\input{tables/scoverage_neg_nopen.tex}
\caption{``Significant" negative discoveries.}
\end{subtable}

\begin{subtable}{\textwidth}
\input{tables/scoverage_pos_nopen.tex}
\caption{``Significant" positive discoveries.}
\end{subtable}

\caption{Table of empirical coverage for nominal 95\% lower credible bounds (methods without the penalty term. }
\end{table}

%\subsubsection*{Reverse asymptotics}
%
%Note that if observation precisions are all similar and most observations are null then all the methods likely to give similar results?
%
%Note: we'd like to make sure it behaves ok in the case where most observations are null.
%Perhaps simulate with 999 null and 1 alternative?
%Also maybe look at performance for small sample sizes - e.g. n=1?
%
%Note that, even though the exact value of the point mass $\pi_0$ cannot, in general, be reliably estimated, the actual underlying distribution $g$ 
%can be quite accurately estimated from the data, provided we assess accuracy by a metric that is not sensitive to $\pi_0$: for example
%by measuring the difference between the true and estimated cumulative distribution function (cdf). See supplementary Figure \ref{} for examples.
%

@@

 We turn now to the second important component of our work: allowing for varying
 measurement precision across units. The key to this is our use of a likelihood,
 (\ref{eqn:normlik}) or (\ref{eqn:tlik}), which explicitly incorporates the measurement precision (standard error) of each $\bhat_j$.

>>>>

\usepackage{sectsty}
\subsectionfont{\normalsize}
\subsubsectionfont{\mdseries\itshape}

@@

To briefly summarize the results in this section:
\begin{enumerate}
\item The UA can produce very different inferences compared with the ZA.
\item The UA can yield conservative estimates of the proportion of true nulls, $\pi_0$, and hence conservative estimates of \lfdr and \FDR.
\item The UA results in a stable procedure, both numerically and statistically, and is somewhat robust to deviations from unimodality.
\end{enumerate}

@@

Figure \ref{fig:ZA} may also be helpful in understanding the interacting role of the UA and the penalty term (\ref{eqn:penalty}) that attempts to make $\pi_0$ as ``large as possible" while remaining consistent with the UA. Specifically, consider the panel of Figure \ref{fig:ZA} that shows \ashr's decomposition of $z$ scores, and imagine increasing $\pi_0$ further. This would increase the null component (dark blue) at the expense of
the alternative component (light blue). Because the null component is $N(0,1)$, and so is biggest at 0, this would eventually create a ``dip" in the light-blue histogram at 0. The role of the penalty term is to push the dark blue component as far as possible, right up to (or, to be conservative, just past) the point where this dip appears. In contrast the ZA pushes the dark blue component until the light-blue component {\it disappears} at 0. See \url{https://stephens999.shinyapps.io/unimodal/unimodal.Rmd} for an interactive
demonstration.

 \subsubsection*{The UA can produce conservative estimates of $\pi_0$}

The illustrative example in Figure \ref{fig:ZA} suggests that the UA will produce smaller estimates of $\pi_0$ than the ZA.
Consequently \ashr will estimate smaller $\lfdr$s and FDRs than existing methods that make the ZA. 
This is desirable, provided that these estimates remain conservative: that is,
that $\pi_0$ does not underestimate the true $\pi_0$ and $\lfdr$ does not underestimate the true $\lfdr$.
The penalty term (\ref{eqn:penalty}) aims to ensure this conservative behaviour. To check its effectiveness
we performed simulations under various alternative scenarios (i.e. various distributions for the non-zero effects,
$g_1$), and values
for $\pi_0$. The alternative distributions are shown in Figure \ref{fig:altdens}, with details in Table \ref{table:scenarios}.
They range from a ``spiky" distribution -- where many non-zero $\beta$ are
too close to  zero to be reliably detected, making reliable estimation of $\pi_0$ essentially impossible -- to a much
flatter distribution, which is a normal distribution with large variance (``big-normal") -- where most non-zero $\beta$ are easily detected
making reliable estimation of $\pi_0$ easier. We also include one asymmetric distribution (``skew"), and one clearly bimodal distribution (``bimodal"),
which, although we view as generally unrealistic, we include to assess robustness of \ashr~to deviations from the UA.

% How do these differences influence estimates of the FDR? To address this, note that  -- in this simple case where the 
% $\shat_j$ are all identical --  the primary driver of differences in FDR estimates among methods is {\it differences in their estimates
% of $\pi_0$}. To see why, observe that, given an estimate $\hat\pi_0$ for $\pi_0$, equation (\ref{eqn:FDRest}) provides a 
% strikingly natural non-parametric estimate for the FDR (provided the denominator is not very small). Thus, 
% although the methods considered here differ from one another in many ways, having estimated $\pi_0$
% they should, if sensible, produce estimates of FDR that agree closely with (\ref{eqn:FDRest}). And, indeed, limited
% empirical checks suggest that this is indeed the case (\url{https://www.github.com/stephens999/ash/examples/qvalue.nonp.rmd}).
%

%Thus, differences in FDR estimates among methods are driven primarily by differences in their estimates of $\pi_0$,
% and so to assess differences in FDR estimates among methods we focus on assessing differences in estimates of $\pi_0$.
%Figure \ref{fig:ZA} suggests that, compared with the ZA, the UA will tend to reduce the estimate of $\pi_0$. 
%At the same time, provided the UA holds, we hope still to provide ``conservative" estimates of $\pi_0$ (that is,
%overestimates of $\pi_0$, which will yield overestimates of the FDR).

\begin{figure} 
\begin{center}
\begin{subfigure}{\textwidth}
	\includegraphics[height=1.8in]{figures/scenarios_density.pdf} 
	\caption{Densities $g_1$ used in simulations.} \label{fig:altdens}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{figures/pi0_est.pdf} 
\caption{Comparison of true and estimated values of $\pi_0$. When the UA holds all methods yield conservative (over-)estimates for $\pi_0$, with \ashr being least conservative, and hence most accurate. When the UA does not hold (``bimodal" scenario) the \ashr estimates are slightly anti-conservative.} \label{fig:pi0sims}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{figures/lfdr_est.png} 
\caption{Comparison of true and estimated \lfdr~from \ashr (ash.n). Black line is $y=x$ and red line is $y=2x$. Estimates of \lfdr~are conservative when UA holds, due to conservative estimates of $\pi_0$.} \label{fig:lfdr}
\end{subfigure}
\begin{subfigure}{\textwidth}
\includegraphics[height=1.8in]{figures/lfsr_est.png} 
\caption{As in c), but for \lfsr~instead of \lfdr. Estimates of \lfsr~are consistently less conservative than \lfdr~when UA holds, and also less anti-conservative in bimodal scenario.}
\end{subfigure}
\end{center}
\caption{Results of simulation studies (constant precision $s_j=1$).} \label{fig:lfsr}
\end{figure}

@@

Figure \ref{fig:pi0sims} compares estimates of $\pi_0$ from \qvalue, \locfdr, \mixfdr and \ashr ($y$ axis) with the true values ($x$ axis). 
For \ashr we show results for $g_1$ modelled as a mixture of normal components (``ash.n") 
and as a mixture of symmetric uniform components (``ash.u"). (Results using the asymmetric uniforms, which we refer to
as ``half-uniforms", and denote ``ash.hu" in subsequent sections, are here generally similar to ash.u and omitted to avoid over-cluttering figures.)
The results show that \ashr provides the smallest more accurate, estimates for $\pi_0$, while remaining conservative
in all scenarios where the UA holds. When the UA does not hold (``bimodal" scenario) the \ashr estimates can be slightly anti-conservative.
We view this as a minor concern in practice, since we view such a strong bimodal scenario as unlikely in most applications where FDR methods
are used. (In addition, the effects on \lfsr estimates turn out to be relatively modest; see below).

@@

\subsubsection*{The lfsr is more robust than lfdr}

The results above show that \ashr can improve on existing methods in producing smaller, more accurate, 
estimates of $\pi_0$ (and, consequently, more accurate estimates of False discovery rates).
Nonetheless, in many scenarios \ashr continues
to substantially over-estimate $\pi_0$ (see the ``spiky" scenario for example). 
The explanation for this is that these scenarios include 
an appreciable fraction of ``small non-null effects" that are essentially indistinguishable from 0, making accurate
estimation of $\pi_0$ impossible. Put another way, and as is well known, $\pi_0$ is not identifiable:
 the data can effectively provide an upper bound on plausible values of $\pi_0$,
but not a lower bound (because the data cannot rule out that everything is non-null, but with miniscule effects).
If we desire conservative behaviour we have to estimate $\pi_0$ by its upper bound, which can
be substantially larger than the true value. 
Since FDR-related quantities depend quite sensitively on $\pi_0$, the consequence of this 
overestimation of $\pi_0$ is corresponding overestimation of FDR (and \lfdr, and $q$ values).
To illustrate, Figure \ref{fig:lfdr} compares the estimated \lfdr~from ash.n with the true value (computed using
Bayes rule from the true $g_1$ and $\pi0$). As predicted, \lfdr~is overestimated, especially in scenarios where 
$\pi_0$ is overestimated. All methods are similarly affected by this, and the ones that most grossly overestimate $\pi_0$ also most grossly overestimated \lfdr and FDR/$q$-values (not shown).

The key point we want to make here is estimation of $\pi_0$, and the accompanying identifiability issues,
 become substantially less troublesome if we use the local false sign rate \lfsr (Section \ref{}), rather than \lfdr, to measure significance. 
 This is essentially because \lfsr is less sensitive to the estimate of $\pi_0$.
To illustrate, Figure \ref{fig:lfsr} compares the estimated \lfsr~from ash.n with the true value: although the estimated \lfsr continue to
be conservative, overestimating the truth, the overestimation is substantially less pronounced than for the \lfdr, especially for
the ``spiky" scenario. Further, in the bi-modal scenario, the anti-conservative behaviour is less pronounced in \lfsr than \lfdr.

We emphasise that, compared with previous debates regarding estimation vs testing, 
this section advances an additional reason for favoring focussing on the sign of an effect
rather than testing whether it is 0. As noted above, many authors have argued to focus on estimation 
because it is implausible that effects are {\it exactly} 0. Here we add that {\it even if one believes
that some effects may be exactly zero}, it is still better to focus on the sign, because generally {\it the data are more informative about that question}
and so inferences are more robust to, say, the inevitable mis-estimation of $\pi_0$.
To provide some intuition, consider an observation with a $z$ score of 0. The \lfdr of this observation can range from 0 (if $\pi_0=0$)
to 1 (if $\pi_0=1$). But, assuming a symmetric $g$, the $\lfsr>0.5$ whatever the value of $\pi_0$, because the observation $z=0$ says
nothing about the sign of the effect.
Thus, are two reasons to use the lfsr instead of the lfdr: it is more generally meaningful (e.g. it applies
whether or not zero effects truly exist),  and estimation of lfsr is more robust.

@@

The EM algorithm, which we use here to fit our model, is notorious for convergence to local optima. 
However, in this case, over hundreds of applications of the procedure, we observed no obvious serious problems 
caused by such behaviour. To quantify this, we ran \ashr 10 times on each of the 600 simulated datasets above using a random initialization for $\pi$,
in addition running it using our default initialization procedure (see Implementation details). We then compared the largest
log-likelihood achieved across all 11 runs with the log-likelihood achieved by the default run.
When using a mixture of normals (ash.n) the results were extremely stable: 96\% showed a negligible log-likelihood difference ($< 0.02$), 
and the largest difference was 0.8. When using mixtures of uniforms (ash.u,ash.hu) results were slightly less stable: 89\% showed a negligible log-likelihood difference ($<0.02$),
and 6\% of runs showed an appreciable log-likelihood difference ($>1$), with the largest difference being 5.0. However, perhaps suprisingly, 
even for this largest difference results from the default run (e.g. the $\lfsr$ values, and the posterior means) were in other ways virtually indistinguishable from the results from the run with the highest log-likelihood \url{github.com/stephens999/ash/dsc-robust/summarize_dsc_robust.rmd}.

@@

Although we have focussed on estimating the FDR, an important advantage of
our EB approach based on modelling the effects $\beta_j$ (rather than $p$ values or $z$ scores)  is that it
can estimate the {\it size} of each effect $\beta_j$.
Specifically, it provides a posterior distribution for each $\beta_j$, which can be used
to construct interval estimates for $\beta_j$ and address question such as ``which effects exceed $T$'', for any 
threshold $T$.
%Importantly, because the posterior distribution for $\beta_j$ depends on the ``prior" effect-size distribution $g$, which is estimated from {\it all} the observations,
%this posterior reflects information from all the observations and not only from the observation $\bhat_j$. 
%In our case, because we assume $g$ to be unimodal about zero, this prior always ``shrinks" the posterior distributions
%towards zero, with the strength of the shrinkage being estimated from the data.
Further, because the posterior distribution is, by definition,
conditional on the observed data, interval estimates based on posterior distributions are also valid Bayesian inferences for any subset of the effects that have
been selected based on the observed data. This kind of ``post-selection" validity is much harder to achieve in the frequentist paradigm.
In particular the posterior distribution solves the (Bayesian analogue of the) ``False Coverage Rate" problem posed by
\cite{benjamini2005false} which \cite{efron2008microarrays} summarizes as follows: ``having applied FDR methods to select a set of nonnull cases,
how can confidence intervals be assigned to the true
effect size for each selected case?". \cite{efron2008microarrays} notes the potential for EB approaches to tackle this problem,
and \cite{zhao2012empirical} consider in detail the case where the non-null effects are normally distributed.
%but also notes the difficulties of implementing a stable general algorithm.

The ability of the EB approach to provide valid ``post-selection" interval estimates is extremely attractive in principle.
But its usefulness in practice
depends on reliably estimating the distribution $g$. Estimating $g$ is a ``deconvolution problem",
which are notoriously difficult to solve in general. Indeed, Efron emphasises
the difficulties of implementing a stable general algorithm, noting in his rejoinder
``the effort foundered on practical difficulties involving the perils of deconvolution... Maybe I am trying
to be overly nonparametric ... but it is hard to imagine a
generally satisfactory parametric formulation..." (\cite{efron2008microarrays} rejoinder, p46).
Our key point here is that the UA greatly simplifies the deconvolution problem.
While not meeting Efron's desire for an entirely general nonparametric approach, we believe 
that the UA can handle many cases of practical interest.

To illustrate this, Figure \ref{fig:egcdf} compares the
estimated $g$ from \ashr  with that from \mixfdr which does not make the UA 
(and which models $g$ as a mixture of $J$ normal distributions, with $J=3$ by default).
The greater reliability of estimates afforded
by the UA is immediately apparent. In particular the estimated cdf from \mixfdr often has an almost-vertical
segment at some non-zero location, indicative of a concentration of density in the estimated $g$ at that location. 
The UA prevents this kind of ``irregular" behaviour, effectively requiring $g$ to be somewhat smooth.
While the UA is not the only way to achieve this, we find it an attractive, simple and effective approach.

Interestingly, even in the ``bimodal" scenario $\ashr$ 
is visually more accurate than \mixfdr: although \mixfdr is capable, in principle, of fitting the multiple modes of $g$, it does not do this well here. 
Possibly the noise level here is sufficiently large to make reliable estimation of the multiple modes difficult. 
Indeed, in multi-modal simulations where the multiple modes are sufficiently well-spaced
to be clearly visible in the observed $\bhat$, \mixfdr fits these modes (Supplementary Information; 
\url{dsc-shrink/check_mixfdr_lownoise.rmd}). Of course, we would not advocate the UA in settings where multi-modality is 
clearly visible in the observed $\bhat$.

We note one caveat on the accuracy of estimated $g$: due to the penalty term (\ref{eqn:penalty}) \ashr tends to systematically
overestimate the mass of $g$ near zero. On careful inspection, this is apparent in Figure \ref{fig:egcdf}: the estimated cdf is generally below the true cdf just to the left of zero,
and above the true cdf just to the right of zero. Averaging the cdf over many replicates confirms this systematic effect (Figure \ref{fig:egcdf}b),
and applying our methods without the penalty term removes this systematic effect, although at the cost of sometimes 
under-estimating $\pi_0$ (Figure \ref{fig:egcdf}c).

@@

\subsubsection*{Calibration of posterior intervals}

To quantify the effects of errors in estimates of $g$ we examine the calibration of the resulting posterior distributions (averaged over 100 simulations in each Scenario). 
Specifically we examine the empirical coverage of nominal lower 95\% credible bounds for a) all observations; b) significant negative discoveries; c) significant positive discoveries.  We examine only lower bounds because the results for upper bounds follow by 
symmetry (except for the one asymmetric scenario). We separately examine positive and negative discoveries because the lower bound plays a different role
in each case: for negative discoveries the lower bound is typically large and negative and limits how big (in absolute value) 
the effect could be; for positive discoveries the lower bound 
is positive, and limits how small (in absolute value) the effect could be. Intuitively, the lower bound for negative discoveries depends on the accuracy of $g$ in its tail,
whereas for positive discoveries it is more dependent on the accuracy of $g$ in the center.

The results are shown in Table \ref{tab:coverage}.  Most of the empirical coverage rates are in the range 0.92-0.96 for nominal coverage of 0.95, which we view
as adequate for practical applications. The strongest deviations from nominal rates are noted and discussed in the table captions.

% As noted above, the penalty term (\ref{eqn:penalty}) causes systematic over-estimation of the mass of $g$ near 0,  which one would expect to overshrink interval estimates towards zero. 
%The effect of overshrinking on the left tail area is different for ``negative discoveries" and ``positive discoveries": for negative discoveries the lower credible bound is negative and overshrinking (moving it too far towards zero) makes the left tail too big; conversely, for positive discoveries, the lower confidence bound is positive, and  
%overshrinking (moving it too far towards zero) makes the tail too small. In the context of reliably identifying ``large" effects we might worry more about under-shrinkage, 
%and be prepared to put up with some overshrinkage to avoid it.

@@

@@

\begin{table}[!ht]
\begin{subtable}{\textwidth}
	\centering\input{tables/scoverage_all.tex}
	\caption{All observations. Coverage rates are generally satisfactory, except for the extreme ``spiky" scenario. This is due to the penalty term (\ref{eqn:penalty}) which tends to cause over-shrinking towards zero. Removing this penalty term produces coverage rates closer to the nominal levels for uniform and normal methods (not shown). Removing the penalty in the half-uniform case is not recommended (see Appendix).}
\end{subtable}

@@

\caption{Table of empirical coverage for nominal 95\% lower credible bounds} \label{tab:coverage}
\end{table}

%\begin{table}[!ht]
%\begin{subtable}{\textwidth}
%	\input{tables/scoverage_all_nopen.tex}
%	\caption{All observations}
%\end{subtable}
%
%\begin{subtable}{\textwidth}
%\input{tables/scoverage_neg_nopen.tex}
%\caption{``Significant" negative discoveries.}
%\end{subtable}
%
%\begin{subtable}{\textwidth}
%\input{tables/scoverage_pos_nopen.tex}
%\caption{``Significant" positive discoveries.}
%\end{subtable}
%
%\caption{Table of empirical coverage for nominal 95\% lower credible bounds (methods without the penalty term. }
%\end{table}
%
%\subsubsection*{Reverse asymptotics}
%
%Note that if observation precisions are all similar and most observations are null then all the methods likely to give similar results?
%
%Note: we'd like to make sure it behaves ok in the case where most observations are null.
%Perhaps simulate with 999 null and 1 alternative?
%Also maybe look at performance for small sample sizes - e.g. n=1?
%
%Note that, even though the exact value of the point mass $\pi_0$ cannot, in general, be reliably estimated, the actual underlying distribution $g$ 
%can be quite accurately estimated from the data, provided we assess accuracy by a metric that is not sensitive to $\pi_0$: for example
%by measuring the difference between the true and estimated cumulative distribution function (cdf). See supplementary Figure \ref{} for examples.
%

@@

 We turn now to the second important component of our work: allowing for varying
 measurement precision across units. The key to this is the use of a likelihood,
 (\ref{eqn:normlik}) or (\ref{eqn:tlik}), that explicitly incorporates the measurement precision (standard error) of each $\bhat_j$.
